Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-05 tex/VHzQ.tex
tex/VHzQ.tex

Previous works \citep[e.g., ][]{Krawczyk2013, Ross2015, Bilick2016} found that cross-matches performed with a radius of 2-3'' between the user catalogue and WISE was a good compromise between completeness and contamination \citep[see e.g. Figure 4 of ][]{Krawczyk2013}. We thus use a cross-match radius of 2.75''. When querying the ALLWISE catalogs, ``Cone Search Radius'' in the ALLWISE table search was set to 2.75'' for the Spatial Constraints. The ``One to One Match'' was ``not'' checked; although possible, we consider it highly unlikely there would be more than one MIR source contributing to the flux of a single UV/optically bright rest-frame quasar. Investigating this in detail is very interesting but left to a future study.

Knowing we have secure detections in the near-infrared bands, and wanting to boost the number of WISE W3/W4 detections, we allow ourselves to be less conservative in querying the ALLWISE catalog and also query the AllWISE Reject Table. However, with the exception of one object (SHELLQs   J1208-0200), the ALLWISE Reject Table does not contain any further W3/W4 detection informationn.

@@

Before reporting on the detection rates, we investigate this effect. Figure~\ref{fig:WISEmag_vs_coverage} shows the WISE magnitude versus signal-to-noise, colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band. In the two shorter bands W1/2 we see the clear and expected trend for brighter objects to have larger SNR, and also for the higher signal to noise for objects with more exposures at a given magnitude. The behaviour for the W3/4 bands is different, with two populations clearly evident in W3 and although a bit more mixed, also in W4. With the suggested split at SNR$>2$, and no obvious R.A./Declination dependence seen, this behaviour is explained by the fact that there are non-detections in W3/4 for objects (with high W1/2 SNR) that are reported in the ALLWISE catalogue.

@@

Recently, \citet{Assef2018} released two large catalogues of AGN 
candidates identified across 30,000 deg$^2$ of extragalactic sky 
from the WISE AllWISE Data Release. The ``R90'' catalogue, is 
contains 4.5M AGN candidates at 90\% reliability (and $\approx$150 
AGN candidates per deg$^2$) while the ``C75'' catalog 
consists of 20.9M AGN candidates at 75\% completeness (and 
($\approx$700 AGN candidates per deg$^2$).  Crossmatching 
out catalogue of 463 VH$z$Qs with these catalogues, produces 
42 matches with	the R90 sample and 98 matches with the C75 sample. 
Both catalogues unsurprisingly match to the ultraluminous quasar 
SDSS J0100+2802 \citep{Wu2015} while the C75, but not the R90 catalogue 
mathes to ULAS J1120+0641 \citep{Mortlock2011}. Neither catalogue 
matches J1342+0928 \citep{Banados2018}.

Very High-$z$ Quasars Detected in WISE W3 and W4.

\begin{figure*}
    \centering
    \subfigure[]{\includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/UHS_J0439+1634.png}} 
    \subfigure[]{\includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}} 
    \subfigure[]{\includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1443+3623.png}}
    \subfigure[]{\includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1623+4705.png}}
    \caption{(a) UHS J0439+1634 
                 (b) SDSS J0100+280 
               (c) SDSS J1443+3623 
 (d) SDSS J1623+4705
}
    \label{fig:foobar}
\end{figure*}
\subsubsection{Individual VH$z$Qs with Interesting MIR properties}

>>>>

Previous works \citep[e.g., ][]{Krawczyk2013, Ross2015, Bilick2016} found that cross-matches performed with a radius of 2-3'' between the user catalogue and WISE was a good compromise between completeness and contamination \citep[see e.g. Figure 4 of ][]{Krawczyk2013}. We thus use a cross-match radius of 2.75''. When querying the ALLWISE catalogues, ``Cone Search Radius'' in the ALLWISE table search was set to 2.75'' for the Spatial Constraints. The ``One to One Match'' was ``not'' checked; although possible, we consider it highly unlikely there would be more than one MIR source contributing to the flux of a single UV/optically bright rest-frame quasar. Investigating this in detail is very interesting but left to a future study.

Knowing we have secure detections in the near-infrared bands, and wanting to boost the number of WISE W3/W4 detections, we allow ourselves to be less conservative in querying the ALLWISE catalogues and also query the AllWISE Reject Table. However, with the exception of one object (SHELLQs  J1208-0200), the ALLWISE Reject Table does not contain any further W3/W4 detection informationn.

@@

Before reporting on the detection rates, we investigate this effect using the AllWISE Source Catalog. Figure~\ref{fig:WISEmag_vs_coverage} shows the WISE ALLWISE magnitude versus signal-to-noise, colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band. In the two shorter bands W1/2 we see the clear and expected trend for brighter objects to have larger SNR, and also for the higher signal to noise for objects with more exposures at a given magnitude. The behaviour for the W3/4 bands is different, with two populations clearly evident in W3 and although a bit more mixed, also in W4. With the suggested split at SNR$>2$, and no obvious R.A./Declination dependence seen, this behaviour is explained by the fact that there are non-detectiopns in W3/4 for objects (with high W1/2 SNR) that are reported in the ALLWISE catalogue.
%%AllWISE Source Catalog

@@

Recently, \citet{Assef2018} released two large catalogues of AGN 
candidates identified across 30,000 deg$^2$ of extragalactic sky 
from the WISE AllWISE Data Release. The ``R90'' catalogue, is 
contains 4.5M AGN candidates at 90\% reliability (and $\approx$150 
AGN candidates per deg$^2$) while the ``C75'' catalogue  
consists of 20.9M AGN candidates at 75\% completeness (and 
($\approx$700 AGN candidates per deg$^2$).  Crossmatching 
out catalogue of 463 VH$z$Qs with these catalogues, produces 
42 matches with	the R90 sample and 98 matches with the C75 sample. 
Both catalogues unsurprisingly match to the ultraluminous quasar 
SDSS J0100+2802 \citep{Wu2015} while the C75, but not the R90 catalogue 
mathes to ULAS J1120+0641 \citep{Mortlock2011}. Neither catalogue 
matches J1342+0928 \citep{Banados2018}.

%\subsubsection{Individual VH$z$Qs with Interesting MIR properties}
Very High-$z$ Quasars Detected in WISE W3 and W4.

\begin{figure*}
    \centering
    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/UHS_J0439+1634.png} 
    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}
    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1443+3623.png}
    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1623+4705.png}
    \caption{ (a) UHS J0439+1634 
                 (b) SDSS J0100+280 
               (c) SDSS J1443+3623 
 (d) SDSS J1623+4705
}
    \label{fig:foobar}
\end{figure*}
